SPENCER THESIS - WORK IN PROGRESS

### 2016-05-17 doc/thesis_swe.tex
Added a few brainstorming notes for new void correction and relevant halos sections.
Added some headings and notes for planned additional sections.

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{mathtools}
%\usepackage{float}
\usepackage[format=plain]{caption}
\usepackage{subcaption}
%\usepackage{multicol}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

@@

@@

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{mathtools}
\usepackage{color}
%\usepackage{float}
\usepackage[format=plain]{caption}
\usepackage{subcaption}
%\usepackage{multicol}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\subsection*{Relevant Halos}
\begin{enumerate}
\item Metric from McCully et al. (cite)
\item Implementation
\item Plot the percent difference between all halos and relevant halos as a function of $\#$ of relevant halos (can adopt relevant-test.py to do this)
\end{enumerate}

\subsection*{Smooth-Component Correction}
\begin{enumerate}
\item Introduce issue
\item Either derive result or state result with derivation in appendix
\item Plots of volume/surface density of halos vs mean universe density
\item Plot distribution of correction kappas
\item Plot distribution of reduced-shear with and without correction
\end{enumerate}

\subsection*{Speedups}
\begin{enumerate}
\item Lookup tables (lensing table)
\item relevant halos
\item pre-calculate grid volumes for s-c correction
\item more plots to quantify speedup times!
\end{enumerate}

@@

\subsection*{Feasibility of Inference}

\subsubsection*{Likelihood Estimation}
\begin{enumerate}
\item Equation from Phil's dissertation
\item Calculate time with and without drilling
\item Time per lensing event, time per lightcone
\end{enumerate}

\subsubsection*{Approximate Bayesian Computation}
\begin{enumerate}
\item Difficult to calculate likelihood, can instead make mock data by samping parameters from prior distribution
\item Come up with `distance' function (compare e-e corr functions) and threshold value
\item Use accepted simulations to approximate posterior
\item Time per ABC
\item Compare time to single lensing event
\end{enumerate}

@@

\subsection*{Smooth-Component Correction Derivation}

\subsection*{TreeCorr to Schneider Proof}
